%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects \& Research Experience }


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\vspace{4 mm}
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Advisor: Dr. Chandra Kant Mishra, IIT Madras} % Advisor
    {Ready-to-use eccentric templates including non-quadrupole modes} % Institution
    {} % Location
    {Aug. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {We focus on developing waveform models for binary black hole inspirals that account for the eccentricity of the orbit. We use the stationary phase approximation and extend it to non-quadrapole moments to develop a ready-to-use fully analytical waveform model. .}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Advisor: Prof. Prasenjit Saha, University of Zurich} % Advisor
    {Polarimetric method for predicting the gravitational wave polarization of LISA verification binaries.} % Institution
    {} % Location
    {Summer 2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Verification binaries are strong gravitational wave sources and fall within the LISA band.
        We are developing a method to predict the various orbital parameters of such binaries using an optical polarimetric method. Our work focuses on the AM CVn type star: HP Librae. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Advisors: Prof. Rajesh Nayak, IISER Kolkata} % Advisor
    {Searching for astrophysical signals in LIGO O1/O2 data} % Institution
    {} % Location
    {Summer 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {The project involved learning the basics of gravitational waves data analysis and parameter estimation
and the theory behind sources of gravitational waves.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Supervisor: Prof. Suresh Govindarajan, IIT Madras} % Advisor
    {SWAN Radio telescope} % Institution
    {} % Location
    {Summer 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {SWAN(Sky Watch Array Network) is a collaborative project by Raman Research Institute, Bangalore
and many national institutes. I learned pulsar observation and data analysis and radio interferometry
through a hands on session program at Gauribidanur radio observatory, Bangalore}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
